---
title: 'Course Project Shiny App and Pitch: Molar solution calculator'
author: "Gabriela Rodriguez"
date: "February 21st, 2018"
output:
  ioslides_presentation: default
  slidy_presentation: default
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## How to prepare a Molar solution of any compound?

- Molar concentration (also called molarity) is a measure of the concentration of a solute in a solution,  in terms of amount of substance per unit volume. A commonly used unit for molar concentration in chemistry is the molarity which is defined as the number of moles per liter (unit symbol: mol/L or m). 
- Molarity is very used in labs, many of the used substances in experiments are reported in this units. Therefore, it is important to calculate how many grams of a substance we need to weight in order to prepare a solution with known molarity.

## The App

- In the present application, done with Shiny, we can calculate how many grams of any substance you need to weight to prepare X milliliters of solution.

- To do the calculus, we need to know 3 variables:
- the molarity 
- the total volume in milliliters 
- the molecular weight of the compound


## How to use the App

* In this App, you'll need to use the sliders to set the Molarity of the solution, the final volume of solution and the molecular weight of the compound you'll use.
* Click the submit button to star the calculus
* At the main Panel you'll be given how many grams of your compound you need to weight

*The App can also be found at https://gabyrod98.shinyapps.io/Myapp/


## Run the App

```{r  echo = FALSE}
library(shiny)
ui <- fluidPage (
  
  
  titlePanel("How many grams do you need to prepare a Molar solution?"),
  sidebarLayout(
    sidebarPanel(
      
      sliderInput("num1", "Final Molarity of your solution (M):",
                  min = 0, max = 10,
                  value = 0, step = 0.1),
      sliderInput("num2", "Total Volume in mililiters:",
                  min = 0, max = 1000,
                  value = 0, step = 0.5),
      sliderInput("num3", "Compound Molecular weight:",
                  min = 0, max = 300,
                  value = 0, step = 0.1),
      submitButton("Submit")),
    # Main panel for displaying outputs ----
    mainPanel(
      
      # Output: Table summarizing the values entered ----
      tableOutput("values"),
      h3("Grams needed to prepare the solution"),
      textOutput("grams")
      
    )))

# Define server logic for sliders 
server <- function(input, output) {
  
  # Reactive expression to create data frame of all input values ----
  sliderValues <- reactive({
    
    data.frame(
      Name = c("Molarity",
               "Volume in mililiters",
               "Molecular weight"),
      Value = as.character(c(input$num1,
                             input$num2,
                             input$num3)),stringsAsFactors=FALSE)})
  
  #Calculus of the grams with the given variables
  
  grams <- reactive({input$num1*input$num2*input$num3/1000})
  
  
  # Show the values in an HTML table ----
  output$values <- renderTable({
    sliderValues()
  })
  output$grams <- renderText({grams()})
  
}

# Create Shiny app ----
shinyApp(ui, server)   

```



